\chapter*{Acknowledgements}
\thispagestyle{empty}

\begingroup\onehalfspacing

I would like to thank Prof. Tilo Baumbach for giving me an opportunity to work with a team of dedicated scientists who use X-rays to reveal the hidden structure of things, and for his constant support. 

I want to express gratitude to Prof. R\"udiger Dillmann for supervising this work in my beloved field of Computer Science.

The interaction with Anton Myagotin and Artem Starostin was a pivotal point for me to start my work in the fields of X-ray Imaging and Image Analysis. Anton was the first one who successfully used optical flow methods for the analysis of time-lapse X-ray images of metal foams. 

Also I want to thank Prof. Joachim Weickert and Prof. Andr\'es Bruhn for introducing me to elegant and very useful variational optical flow methods.

This work would not be possible without insightful and fruitful collaboration with many scientists from various research fields. Among them are Anton Myagotin, Lukas Helfen, Alexander Rack, Simon Zabler, Ralf Hofmann, Jubin Kashef, Julian Moosmann, Venera Weinhardt, Thomas van de Kamp, Tomy dos Santos Rolo, Tom\'a\v{s} Farago, Dmitry Karpov, Martin K\"ohl and Tilo Baumbach.
It was a pleasure to work with them. I have learned so much along the way.

Many thanks goes to Martin K\"ohl for proofreading and useful feedback. I incorporated almost all his suggestions.

Igor Karlinskiy made a great contribution by helping me to implement optical flow methods on GPUs and visualization of 3D vector fields. He also assisted to create good-looking diagrams and analysis plots.

I appreciate many pleasing conversations, disputes and our fun teamwork with Dmitry Karpov.

And last but not least, I want to thank my family for their patience and infinite support. 

\endgroup


%\clearpage